---
title: "Jim's Project Log"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Projects"
    theme: cosmo
    code-fold: true
    self-contained: true
  pdf:
    toc: true
execute:
  echo: false
  warning: false
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

# Overview

This document tracks active projects, sub-tasks, and progress notes.
Update the status column and log entries regularly to maintain momentum.

```{r summary-table}
projects <- data.frame(
  Project = c(
    "R Sampler",
    "spmR",
    "WtAgeRE",
    "ADMB pm.tpl",
    "SporC (age-error)",
    "SporC (two-area)",
    "Admin"
  ),
  Status = c(
    "In Progress",
    "In Progress",
    "To Do",
    "In Progress",
    "To Do",
    "In Progress",
    "To Do"
  ),
  Priority = c("High","High","Medium","High","Medium","High","Low"),
  Notes = c(
    "Testing underway; age-error and data pulls pending",
    "Testing underway; alt inputs, speed, F-SPR needed",
    "Age-error development not yet started",
    "Updating 2024 base run to 2025 data",
    "Specs needed before implementation",
    "Check Russian results; develop defaults",
    "Tomo form outstanding"
  )
)

kable(projects, caption = "Project Status Summary", align = c("l","c","c","l")) |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"), full_width = FALSE) |>
  column_spec(2,
    color = ifelse(projects$Status == "Done", "white",
             ifelse(projects$Status == "In Progress", "white", "#555")),
    background = ifelse(projects$Status == "Done", "#5a9c6f",
                 ifelse(projects$Status == "In Progress", "#d6a435", "#ddd"))
  )
```

---

# Projects

## R Sampler

**Status:** In Progress
**Goal:** Validate and extend the R-based sampler.

### Sub-tasks

| Task | Status |
|------|--------|
| Core testing of sampler | 🔄 In Progress |
| Add age-error module | ⬜ To Do |
| Data pulls required for testing | ⬜ To Do |

### Progress Notes

<!-- Add dated entries below as you work on this project -->

> *2026-02-20 — Project log initiated. Core testing is the current focus.*

---

## spmR

**Status:** In Progress
**Goal:** Test and extend the `spmR` surplus production model package.

### Sub-tasks

| Task | Status |
|------|--------|
| Core testing | 🔄 In Progress |
| Alternative model inputs | ⬜ To Do |
| Speed comparisons vs. ADMB | ⬜ To Do |
| F-SPR calculations in R | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Project log initiated.*

---

## WtAgeRE (Age-error)

**Status:** To Do
**Goal:** Develop age-error functionality for the `WtAgeRE` model.

### Sub-tasks

| Task | Status |
|------|--------|
| Design age-error specification | ⬜ To Do |
| Implement in model | ⬜ To Do |
| Test and validate | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Project log initiated. Not yet started.*

---

## ADMB pm.tpl (2025 Update)

**Status:** In Progress
**Goal:** Update the vanilla 2024 `pm.tpl` ADMB run to use 2025 data.

### Sub-tasks

| Task | Status |
|------|--------|
| Confirm 2024 base run is clean | ⬜ To Do |
| Swap in 2025 data inputs | ⬜ To Do |
| Verify model convergence | ⬜ To Do |
| Document changes | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Project log initiated.*

---

## SporC — Age-error Specs

**Status:** To Do
**Goal:** Define and implement age-error specifications within SporC.

### Sub-tasks

| Task | Status |
|------|--------|
| Draft age-error specs document | ⬜ To Do |
| Review with team | ⬜ To Do |
| Implement in SporC | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Project log initiated. Specs need to be drafted first.*

---

## SporC — Two-area Version

**Status:** In Progress
**Goal:** Build and validate a two-area spatial version of SporC.

### Sub-tasks

| Task | Status |
|------|--------|
| Develop two-area framework | 🔄 In Progress |
| Review Russian assessment results | ⬜ To Do |
| Develop default parameter values | ⬜ To Do |
| Validate against single-area results | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Project log initiated.*

---

## Admin

**Status:** To Do

### Sub-tasks

| Task | Status |
|------|--------|
| Fill out Tomo form | ⬜ To Do |

### Progress Notes

> *2026-02-20 — Outstanding item.*

---

# Weekly Check-in Template

Use this section at the start of each week to log what you worked on and what's next.

## Week of: ___________

**Completed this week:**

-

**In progress / carried forward:**

-

**Blocked on:**

-

**Next week's focus:**

1.
2.
3.

---

*Tip: keep this file in version control (git) so you have a timestamped history of progress entries.*
